Visually pleasing knot projections

### 2021-09-24 inst/jma_knot.tex
fixes #23

Here, knot paths are required to have Bezier handles that are
symmetrically placed with regard to nodes (this is a user-settable
option in inkscape).  Although radius of curvature is not necessarily
matched at either side of a node, visual continuity of the strand is
ensured.  In the diagram, strand crossing points are far from nodes,
as this ensures visual continuity of strands at crossing points,
especially the understrand.

>>>>

Here, knot paths are required to have Bezier handles that are
symmetrically placed with regard to nodes (this is a user-settable
option in inkscape).  Although radius of curvature is not necessarily
matched at either side of a node, visual continuity of the strand is
thereby ensured near the node.  At a crossing point it is important
that both the unbroken and broken strands (designated ``overstrand''
and ``understrand'' respectively) are smooth.  We would like strand
crossing points to be far from nodes, as this ensures visual
continuity of strands at crossing points, especially the understrand.
